---
title: "Enhanced Text Editor"
author: "Matt Kumar"
date: "`r Sys.Date()`"
output:
  html_document:
    theme:
      bootswatch: sketchy
runtime: shiny
resource_files:
- inst/icons.svg
- inst/trumbowyg.colors.min.css
- inst/trumbowyg.colors.min.js
- inst/trumbowyg.emoji.min.js
- inst/trumbowyg.fontsize.min.js
- inst/trumbowyg.min.css
- inst/trumbowyg.min.js
- inst/trumbowyg_binding.js
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(emo)
library(shiny)

source("trumbowygInput.R")

# define what buttons you would like on the widget
btn_list <- list('strong', 'em', 'underline',
                 'foreColor', 'backColor', 
                 'fontsize',
                 'emoji',
                 'formatting',
                 'undo', 
                 'redo',
                 'superscript', 'subscript',
                 'link',
                 'justifyLeft', 'justifyCenter', 'justifyRight',
                 'unorderedList', 'orderedList',
                 'fullscreen')

```

## Trumbowyg.js
[Trumboywg.js](https://alex-d.github.io/Trumbowyg) is a lightweight, what-you-see-is-what-you-get, text editor written in javascript. I've adapted it for use in `rmarkdown` and `shiny` applications, potentially for my work, but mostly for fun. 

```{r, echo=F}
HTML('<p>In addition to the default options, I’ve included support for some official plugins, namely <strong><span style=\"color: rgb(79, 129, 189);\">t</span><span style=\"color: rgb(192, 80, 77);\">e</span><span style=\"color: rgb(155, 187, 89);\">x</span><span style=\"color: rgb(247, 150, 70);\">t</span> <span style=\"color: rgb(149, 55, 52);\">c</span><span style=\"color: rgb(255, 255, 0);\">o</span>l<span style=\"color: rgb(192, 145, 0);\">o</span><span style=\"color: rgb(128, 100, 162);\">r</span><span style=\"background-color: rgb(255, 255, 255); color: rgb(183, 221, 232);\">i</span></strong><span style=\"color: rgb(192, 80, 77);\">n</span><strong style=\"color: rgb(147, 137, 83);\">g</strong>,&nbsp;<span style=\"background-color: rgb(183, 221, 232);\"> text highlighting</span> and &nbsp;&nbsp;<br></p>') 
```
emoji's! `r emo::ji("smile")`. 


## Try it
```{r eruptions, echo=FALSE}
trumbowygInput("editor", 
                label = "Editor, all options enabled",
                value = "try me!",
                btns = btn_list)

```


## Under the Hood

The underlying `html` code for your formatted text is returned here. It is accessible server side in R for your applications.

```{r tabsets, echo=FALSE}
output$html <- renderPrint(input$editor)
verbatimTextOutput('html')
```


## Download File

You can save what you've made in the editor as a `rmarkdown` html file.

```{r download, echo=FALSE}
# https://stackoverflow.com/questions/42866055/rshiny-download-button-within-rmarkdown
downloadButtonRmd <- function (outputId, label = "Download", class = NULL, ...)  {
     tags$a(id = outputId, class = paste("btn btn-default shiny-download-link", 
        class), href = "", target = "_blank", download = NA, 
        icon("download"), label, ...)
}

# https://shiny.rstudio.com/articles/generating-reports.html
    output$report <- downloadHandler(
        filename = "report.html",
        content = function(file) {
            tempReport <- file.path(tempdir(), "report.Rmd")
            file.copy("report.Rmd", tempReport, overwrite = TRUE)
            params <- list(n = input$editor)
            rmarkdown::render(tempReport, output_file = file,
                              params = params,
                              envir = new.env(parent = globalenv())
            )
        }
    )
downloadButtonRmd('report','Render Example')
```

## More
You can see the code on my github repository [here](https://github.com/mattkumar/shinyTrumbowyg)

